Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-17 paper.tex
Some work on introduction; still very rough

Previously we took a general look at how maximum performance and some 2D wake
profiles are affected by Reynolds number, but here we week to look much deeper.

In this study we set out to measure the effects of scale, both Reynolds and
Froude scales, on the performance of the turbine, and its near-wake
characteristics.

>>>>

Previously we took a general look at how maximum performance and some 2-D wake
profiles are affected by Reynolds number, but here we look deeper. In this study
we set out to measure the effects of scale, i.e. Reynolds number on the
performance of the turbine, and its near-wake characteristics. We were looking
to find a threshold scale beyond which a physical model study could reliably
predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.
